%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Vaishak Krishna} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 908-938-4296 ~ \href{mailto:vaishak.krishna@berkeley.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{vaishak.krishna@berkeley.edu}} ~ 
    \href{https://linkedin.com/in/vaishakkrishna/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/vaishakkrishna}}  ~
    \href{https://github.com/vaishakkrishna}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/vaishakkrishna}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
  {University of California, Berkeley (GPA: 3.86/4.0)}{Aug. 2020 -- Present}
      {In progress: Bachelor of Arts in Computer Science}{Berkeley, California}
    \vspace{-5pt}
      \item{Awards/Honors: Dean's list, Upsilon Pi Epsilon CS Honor Society.}

  \resumeSubHeadingListEnd   
  
%------RELEVANT COURSEWORK-------
\vspace{-16pt}
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{2}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Discrete Mathematics and Probability
                \item Structure and Interpretation of Computer Programs
                \item Algorithms and Intractable Problems
                \item Computer Architecture
                \item Designing Information Devices and Systems
                \item In progress: Operating Systems
                \item In progress: Foundations of Data Science
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Computer Science Mentors}{January 2022 -- May 2022}
      {Mentor}{Berkeley, California}
      \resumeItemListStart
        \resumeItem{Taught data structures concepts as a mentor to five students weekly with an effectiveness rating of \textbf{4.5/5.0}.}
        \resumeItem{Co-led a task force to \textbf{teach class of 20} computer science students about concepts in ``Git'' and ``GitHub''.}
        \resumeItemListEnd
    \resumeSubheading
      {QBurst}{June 2021 -- July 2021}
      {Backend Software Engineer Intern}{Remote}
      \resumeItemListStart
      \resumeItem{Implemented three \textbf{REST API} methods to view/add customer lead data using the .NET framework and SQL server.}
    \resumeItemListEnd

    \resumeSubheading
      {Gifted Gabber}{June 2022 -- August 2022}
      {Research Assistant under Dr.Rajagopal Appavu}{Remote}
      \resumeItemListStart
        \resumeItem{Procured men's prostate cancer \textbf{data sets} and clinical trial results for data visualization and drug efficacy analysis.}
        \resumeItem{\textbf{Established effective student/professor lines of communication} for a 50\% reduction in student emails.}
    \resumeItemListEnd

    

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Wordle Improved} $|$ \href{https://wordlem.top}{\underline{https://wordlem.top}} $|$\emph{JavaScript, React, HTML/CSS, Cloud Computing}}{May 2022 - August 2022}
          \resumeItemListStart
            \resumeItem{Launched a \textbf{responsive, improved} version of the hit game ``Wordle'' using ReactJS, hosted in cloud servers.}
            \resumeItem{Construced a \textbf{\boldmath{$<$} 5 second} information theory solver that is \textbf{\boldmath{$97\%$} as good} as the current best solver (3.54 avg guesses).}
            \resumeItem{Ensured compatibility with \textbf{multiple operating systems and browsers} using various Web APIs.}
            \resumeItem{Deployed the web app for \textbf{400+ visitors} by configuring \textbf{Apache HTTP server} on Linux machines in the \textbf{cloud}.}
            \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
      {\textbf{EVA Poker AI} $|$ \emph{C++, Java, Python}}{July 2022 - Present}
      \resumeItemListStart
            \resumeItem{Co-Developed an \textbf{efficient and intuitive} command-line Texas Hold-em poker simulator in Python for 2-8 players.}
            \resumeItem{Created an \textbf{AI solver} for Kuhn Poker in C++ with   using an iterative regret-minimizing algorithm. }
            \resumeItem{Designed a \textbf{novel version of Poker} to aid the eventual development and debugging of the Texas hold-em solver.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{School Projects} $|$ \emph{Python, Java, C}}{October 2020}
          \resumeItemListStart
          \resumeItem{Developed a \textbf{genetic optimization algorithm} in Python for a project to achieve a ranking of \textbf{5th place out of 220.}}
          \resumeItem{Programmed a two-player PVP game with random world generation in Java using \textbf{object-oriented principles.}}
          \resumeItem{Implemented \textbf{voice recognition} for a robot car in C using \textbf{SVD and Machine Learning} to classify sound waves.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Computer Languages}{: Python, JavaScript, Java/JUnit, RISC-V Assembly, C/C++, HTML, CSS, C\#} \\
      \textbf{Developer Tools}{: VS Code, IntelliJ, PyCharm, Eclipse, Visual Studio} \\
     \textbf{Technologies/Frameworks}{: ReactJS, Git/GitHub, Chrome Developer Tools, Jyupiter Notebook, .NET, Django} \\
    }}

 \end{itemize}
 \vspace{-16pt}
 
 

%-----------INVOLVEMENT---------------
\section{Other Skills/Hobbies}

    \begin{itemize}
      
      \setlength\itemsep{-1pt}
      \item\small{Languages: English (Bilingual Proficiency), Malayalam (Bilingual Proficiency), Hindi (Limited Working Proficiency), Mandarin Chinese (Limited Working Proficiency)}
      \item{Trombone Performance - accepted/performed in various ensembles at the school, state, and all-national levels.}
      \item{Hobbies - Computer Hardware, Weight Lifting, Rubik's Cubing, Video Games.}
    \end{itemize}
                


\end{document}
